Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-08-18 draftfinalreport_v4.Rnw
revisions based on new B/C with mean of 5 years of cases used
added a figure and a table with bc analyses
This will be additional figure and table, showing effect of cost of
immunising population and bc

@@

>>>>

vacp_rv<-read.csv("tables/rv.csv",header=T)

@@

\begin{sidewaystable}\small
<<results=tex,echo=FALSE>>=
colnames(costtable74)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C")
costtable74[,2:10] <- round(costtable74[,2:10])
costtable74[,11] <- round(costtable74[,11],2)
latex(costtable74, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 74 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}  is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio.}
\label{table:cost74}
\end{sidewaystable}

\begin{figure}
     \centering
     \includegraphics[width=0.9\textwidth]{figures/bc.pdf}
     \caption{The relationship between the benefit--cost ratio and the cost of immunising individuals in the New Zealand population. The mean number of measles cases per years since 2009 was used the expected number of cases prevented from the additional vaccination (\autoref{table:cost20},\autoref{table:cost50},\autoref{table:cost74}).}
     \label{fig:bc}
\end{figure}
